A multi-scale story of the diffusion of a new technology: the web

### 2024-06-11 presentations/web_diffusion.Rmd
path

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->
![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->
![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/oa_ggplot/morani_la.csv")

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/oa_ggplot/lisa/")

@@

|                   | RMSE  | RSquared | MAE   |
|-------------------|-------|----------|-------|
| Local Authorities* | 0.032 | 0.810    | 0.019 |
| Output Areas       | 5.000 | 0.205    | 1.047 |

<small>
*No retail centre predictors for the Local Authority models
</small>

@@

|                   | RMSE  | RSquared | MAE   |
|-------------------|-------|----------|-------|
| Local Authorities* | 0.200 | 0.634    | 0.148 |

<small>
*No retail centre predictors for the Local Authority models
</small>

>>>>

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/la_ggplot/morani_la.csv")

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/la_ggplot/lisa/")

@@

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.032 | 0.810    | 0.019 |
| Output Areas        | 5.000 | 0.205    | 1.047 |

<small> \*No retail centre predictors for the Local Authority models
</small>

@@

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.200 | 0.634    | 0.148 |

<small> \*No retail centre predictors for the Local Authority models
</small>
